### 2016-04-27 ch02-qlogms/excitation-design.tex
Improved MC figures
Fix some references
Some work on conclusions
More conclusion + small stuff everywhere

  \begin{example} \label{eg:excitation:quasilogarithmicGrid:matlab}
  An easy way to produce a quasi-logarithmic grid in \MATLAB is to first produce the logarithmic grid \code{fLog} as in  \egref{eg:excitation:logarithmicGrid:matlab} and reducing it to a quasi-logarithmic grid with resolution $\Delta f$ using \mcode[mathescape]{f = unique(round(fLog/$\Delta f$))*$\Delta f$}.
  Note that this is a computationally efficient way since both \mcode{logspace} and \mcode{unique} require at most $\bigO{ F }$ time, where \mcode[mathescape]{$F\;$ = numel(fLog)}.
  \end{example}

@@

  \begin{table}
  \centering
  \label{tbl:excitation:gridProperties}
   \caption{Summary of  properties of the different frequency grids.}
    \begin{tabular}{rccc} 
    \toprule
     & \textsc{Linear} & \textsc{Logarithmic} & \textsc{Quasi-logarithmic} \\
    \midrule
    % Limits & \multicolumn{3}{c}{$\ClosedInterval{\fMin, \fMax}$}\\
    Properties 
       & $f_0, \Delta f$ 
       & $f_0, \alpha$ 
       & $f_0, \Delta f, \alpha$\\
    \midrule
    $f_{k+1} \isdef$ 
       & $f_{k} + \Delta f$ 
       & $\alpha f_{k}$
       & $\round{\frac{\alpha^{N_k} f_k}{\Delta f}} \Delta f$,   $N_k \in \NaturalNumbersWithoutZero$
       \\[5pt]
    $\Delta f_k \isdef f_{k+1} - f_k$ 
       & $\Delta f$
       & $(\alpha - 1) f_k$
       & $ \in \NaturalNumbersWithoutZero \Delta f$ \\[5pt]
    $\alpha_k \isdef \frac{f_{k+1}}{f_k}$ 
       & $1 + \frac{\Delta f}{f_k}$ 
       & $\alpha$ 
       & $\approx \alpha $ \\[5pt]
    $F_{\ClosedInterval{a,b}}$
       & $\floor{\frac{b - a}{\Delta f}}$
       & $\floor{\log_{\alpha} \frac{b}{a}}$
       & $\approx \floor{\log_{\alpha} \frac{b}{a}}$\\[5pt]
    $F_{\ClosedInterval{f, \kappa f}}$
      & $\floor{\frac{(\kappa - 1)f}{\Delta f}}$
      & $\floor{\log_{\alpha} \kappa}$
      & $\approx \floor{\log_{\alpha} \kappa}$\\[5pt]
    \bottomrule
    \end{tabular}
  \end{table}

@@

  Taking this into account allows to limit the study of second order systems to a small set of systems that should be considered in the search for a suitable grid spacing $\alpha$.
  We can limit the evaluation of the theoretical uncertainty \eqref{eq:excitation:varPeak} obtained by exciting the system with a logarithmic signal with ratio $\alpha$ to the analysis of second order systems with a resonance frequency set to
  \begin{equation}
    \wn \alpha^{N+\gamma}\qquad \text{ with } 0 \leq \gamma < 1\text{.}
    \label{eq:excitation:theoreticalBestVariationOmega}
  \end{equation}
  The value $\gamma$ is varied for a fixed value of $N \in \ZN$.
  The value of $N$ will not influence the `shape` (and uncertainty) of the FRF.

@@

  \begin{figure}[th]
    \centering
      \setlength\figurewidth{0.68\columnwidth}
      \setlength\figureheight{0.68\figurewidth}
    \input{\thisDir/figs/Sys02-4.tikz}
    \caption[Simulated \gls{FRF} of a single system using different excitation signals.]{\gls{FRF}~\legref{leg:excitation:sim:FRF} of a second order system with $\fR=40\unit{Hz}$ and $\damping=0.2$ along with the corresponding variance and bias of the parametric models obtained using three different kinds of multisine excitations.}%
    \label{fig:excitation:FRF1}
  \end{figure}

@@

  \begin{figure}%
    \centering
      \setlength\figurewidth{0.68\columnwidth}
      \setlength\figureheight{0.68\figurewidth}
    \input{\thisDir/figs/damping02-cmp.tikz}
    \caption[Simulated \glspl{FRF} of systems with damping $0.2$ for different excitation signals.]{%
       \Glspl{FRF} for different second order systems with constant damping $\damping=0.2$ but different resonance frequencies. 
       Comparison of the variance around the respective resonance frequency reveals the performance of each excitation signal.}%
    \label{fig:excitation:damping02}
  \end{figure}

@@

  \begin{figure}%
    \centering
      \setlength\figurewidth{0.68\columnwidth}
      \setlength\figureheight{0.68\figurewidth}
    \input{\thisDir/figs/damping005-cmp.tikz}
    \caption[Simulated \glspl{FRF} of systems with damping $0.05$ for different excitation signals.]{\Glspl{FRF} for different second order systems with constant damping $\damping=0.05$ but different resonance frequencies. 
    Comparison of the variance around the respective resonance frequency reveals the performance of each excitation signal.}%
    \label{fig:excitation:damping005}
  \end{figure}

@@

\begin{figure}%
  \centering
  \setlength\figurewidth{0.68\columnwidth}
  \setlength\figureheight{0.68\figurewidth}
  \input{\thisDir/figs/Sum02log0-2.tikz}
  \caption[Simulated FRF of sum of two sub-systems.]{FRF for the sum of two second order systems with $\damping=0.2$ and            resonances at $ 400 \unit{Hz}$ and 4 \unit{kHz} as observed by a quasi-logarithmic multisine.}%
  \label{fig:excitation:sumSys}
\end{figure}

>>>>

  \begin{example} \label{eg:excitation:quasilogarithmicGrid:matlab}
  An easy way to produce a quasi-logarithmic grid in \MATLAB is to first produce the logarithmic grid \code{fLog} as in  \egref{eg:excitation:logarithmicGrid:matlab} and reducing it to a quasi-logarithmic grid with resolution $\Delta f$ using \mcode[mathescape]{f = unique(round(fLog/$\Delta f$))*$\Delta f$}.
  Note that this is a computationally efficient way since both \mcode{logspace} and \mcode{unique} require at most $\bigO{ F }$ time, where \mcode[mathescape]{$F\;$ = numel(fLog)}.
  % computational complexity: 
  % `logspace` := O(F) in both time and space (just a for-loop)
  % `unique` := O(F) in both time and space (values are sorted beforehand, so just for-loop, flag items that are equal to the last and return unflagged items)
  \end{example}

@@

  \begin{table}
  \centering
   \caption{Summary of  properties of the different frequency grids.}
   \label{tbl:excitation:gridProperties}
    \begin{tabular}{rccc} 
    \toprule
     & \textsc{Linear} & \textsc{Logarithmic} & \textsc{Quasi-logarithmic} \\
    \midrule
    % Limits & \multicolumn{3}{c}{$\ClosedInterval{\fMin, \fMax}$}\\
    Properties 
       & $f_0, \Delta f$ 
       & $f_0, \alpha$ 
       & $f_0, \Delta f, \alpha$\\
    \midrule
    $f_{k+1} \isdef$ 
       & $f_{k} + \Delta f$ 
       & $\alpha f_{k}$
       & $\round{\frac{\alpha^{N_k} f_k}{\Delta f}} \Delta f$,   $N_k \in \NaturalNumbersWithoutZero$
       \\[5pt]
    $\Delta f_k \isdef f_{k+1} - f_k$ 
       & $\Delta f$
       & $(\alpha - 1) f_k$
       & $ \in \NaturalNumbersWithoutZero \Delta f$ \\[5pt]
    $\alpha_k \isdef \frac{f_{k+1}}{f_k}$ 
       & $1 + \frac{\Delta f}{f_k}$ 
       & $\alpha$ 
       & $\approx \alpha $ \\[5pt]
    $F_{\ClosedInterval{a,b}}$
       & $\floor{\frac{b - a}{\Delta f}}$
       & $\floor{\log_{\alpha} \frac{b}{a}}$
       & $\approx \floor{\log_{\alpha} \frac{b}{a}}$\\[5pt]
    $F_{\ClosedInterval{f, \kappa f}}$
      & $\floor{\frac{(\kappa - 1)f}{\Delta f}}$
      & $\floor{\log_{\alpha} \kappa}$
      & $\approx \floor{\log_{\alpha} \kappa}$\\[5pt]
    \bottomrule
    \end{tabular}
  \end{table}

@@

  Taking this into account allows to limit the study of second order systems to a small set of systems that should be considered in the search for a suitable grid spacing $\alpha$.
  We can limit the evaluation of the theoretical uncertainty \eqref{eq:excitation:varPeak} obtained by exciting the system with a logarithmic signal with ratio $\alpha$ to the analysis of second order systems with a resonance frequency set to
  \begin{equation}
    \wn \alpha^{N+\gamma}\qquad \text{ with } 0 \leq \gamma < 1\text{.}
    \label{eq:excitation:theoreticalBestVariationOmega}
  \end{equation}
  The value $\gamma$ is varied for a fixed value of $N \in \ZN$.
  The value of $N$ will not influence the `shape` (and uncertainty) of the \gls{FRF}.

@@

  \begin{figure}[th]
    \centering
      \setlength\figurewidth{0.68\columnwidth}
      \setlength\figureheight{0.68\figurewidth}
    \input{\thisDir/figs/Sys02-4.tikz}
    \caption[Simulated \glsentryshort{FRF} of a single system using different excitation signals.]{\gls{FRF}~\legref{leg:excitation:sim:FRF} of a second order system with $\fR=40\unit{Hz}$ and $\damping=0.2$ along with the corresponding variance and bias of the parametric models obtained using three different kinds of multisine excitations.}%
    \label{fig:excitation:FRF1}
  \end{figure}

@@

  \begin{figure}%
    \centering
      \setlength\figurewidth{0.68\columnwidth}
      \setlength\figureheight{0.68\figurewidth}
    \input{\thisDir/figs/damping02-cmp.tikz}
    \caption[Simulated \glsentryshortpl{FRF} of systems with damping $0.2$ for different excitation signals.]{%
       \Glspl{FRF} for different second order systems with constant damping $\damping=0.2$ but different resonance frequencies. 
       Comparison of the variance around the respective resonance frequency reveals the performance of each excitation signal.}%
    \label{fig:excitation:damping02}
  \end{figure}

@@

  \begin{figure}%
    \centering
      \setlength\figurewidth{0.68\columnwidth}
      \setlength\figureheight{0.68\figurewidth}
    \input{\thisDir/figs/damping005-cmp.tikz}
    \caption[Simulated \glsentryshortpl{FRF} of systems with damping $0.05$ for different excitation signals.]{\Glspl{FRF} for different second order systems with constant damping $\damping=0.05$ but different resonance frequencies. 
    Comparison of the variance around the respective resonance frequency reveals the performance of each excitation signal.}%
    \label{fig:excitation:damping005}
  \end{figure}

@@

\begin{figure}%
  \centering
  \setlength\figurewidth{0.68\columnwidth}
  \setlength\figureheight{0.68\figurewidth}
  \input{\thisDir/figs/Sum02log0-2.tikz}
  \caption[Simulated \glsentryshort{FRF} of sum of two sub-systems.]{\gls{FRF} for the sum of two second order systems with $\damping=0.2$ and            resonances at $ 400 \unit{Hz}$ and 4 \unit{kHz} as observed by a quasi-logarithmic multisine.}%
  \label{fig:excitation:sumSys}
\end{figure}

### 2016-04-27 ch03-lrm/nonparametric.tex
Fix some references
More conclusion + small stuff everywhere

\begin{figure}
  \centering
  \remakeNextFigure
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.62\figurewidth}
  \input{\thisDir/figs/MC-SNR40-NBW64and8.tikz}
  \caption[Bias, variance for $\nBW\in{8,64}$ at $\SNR=40\unit{dB}$]{The bias, variance and \gls{RMS} error of the different estimators is shown for $\SNR= 40 \unit{dB}$ and $\nBW \in \set{8,64}$ samples in the $3 \unit{dB}$ bandwidth of the system (as highlighted).}
  \label{fig:nparam:mc:singleTuple}
\end{figure}

>>>>

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.62\figurewidth}
  \input{\thisDir/figs/MC-SNR40-NBW64and8.tikz}
  \caption[Bias, variance for $\nBW \in \set{8,64}$ at $\SNR=40\unit{dB}$]{The bias, variance and \gls{RMS} error of the different estimators is shown for $\SNR= 40 \unit{dB}$ and $\nBW \in \set{8,64}$ samples in the $3 \unit{dB}$ bandwidth of the system (as highlighted).}
  \label{fig:nparam:mc:singleTuple}
\end{figure}

### 2016-04-27 ch03-lrm/truncation.tex
More conclusion + small stuff everywhere

The estimation of $\hat{G}_{\LPM}(\omega_k)$ at a single frequency $\omega_k = 0.586\unit{Hz}$ is illustrated in \figref{LPM_Schematic_EG}.% centered at $k$, where $r = 0$.
\begin{figure}[htb] %  figure placement: here, top, bottom, or page
   \centering
   \setlength{\figurewidth}{0.8\columnwidth}
   \setlength{\figureheight}{0.68\figurewidth}

   \input{\thisDir/figs/LPMfig.tikz}
   \caption[Illustration of the LPM.]{Illustration of the \gls{LPM}. Top figures: input spectrum (left) and output spectrum (right). 
   A small band is selected (gray area), in which $\hat G_{\LPM}(\omega_{k+r})$ is estimated (black thick line, bottom figure) as a local polynomial. Only its central value $\hat G_{\LPM}(\omega_k)$ (white circle) is retained. This procedure is repeated for all frequencies $\omega_k$.}
   \label{LPM_Schematic_EG}
\end{figure}
This procedure is repeated at each central frequency $\omega_k$ for  $k\in \Set{1,\dots,N/2}$ (i.e. the entire frequency band, including Nyquist, but excluding \gls{DC}, and regularizing at the boundaries). This completes the \gls{LPM}, yielding an intrinsic averaging of the spectra of the estimated \gls{FRF}, $\hat{G}_{\LPM}(\omega_k)$.

@@

\end{enumerate}
This procedure is illustrated in \figref{fig:nparam:trunc:nonparametric:truncation:Ftest} for the system described by the following simulation equations, which are relevant to the LPM outlined in Section \ref{sec:nparam:trunc:LPMFRFest}:
\begin{subequations}
\label{eq:systemSimulations}
\begin{align}
y_0(t)  &= 1.5371y_0(t-1)    -0.9025y_0(t-2) + u(t)\\
y(t)       &= y_0(t) + e(t),
\end{align}
\end{subequations}
where $e(t)$ is a white noise sequence, such that the SNR of the output signal is 78.2~dB.
% \eqref{eq:systemSimulations}. 
The figure shows segments of the estimated impulse response. The last two segments are dominated by the noise, while all samples at $t<80$ have large system contributions. The algorithm outlined above selects $\truncTime = 80$, beyond which all samples are set to zero, resulting in a smoothed \gls{FRF} estimate.

@@

\figref{fig:nparam:trunc:LPMvsTRunc} and \figref{fig:nparam:trunc:pdfAndRMSeVStruncTime} compare the \gls{LPM} with and without truncation of the impulse response.
Here, the truncation instant $\truncTime$ is determined using the exponential fitting method.
They were obtained from simulations on  the system described by the following simulation equations, which are relevant to the \gls{LPM} outlined in \secref{sec:nparam:trunc:LPMFRFest}:
\begin{subequations}
\label{eq:systemSimulations}
\begin{align}
y_0(t)  &= 1.5371y_0(t-1)    -0.9025y_0(t-2) + u(t)
\\
y(t) &= y_0(t) + e(t),
\end{align}
\end{subequations}
where $e(t)$ is a white noise sequence, such that the \gls{SNR} of the output signal is $18.3\unit{dB}$.

>>>>

The estimation of $\hat{G}_{\LPM}(\omega_k)$ at a single frequency $\omega_k = 0.586\unit{Hz}$ is illustrated in \figref{LPM_Schematic_EG}.% centered at $k$, where $r = 0$.
\begin{figure}[htb] %  figure placement: here, top, bottom, or page
   \centering
   \setlength{\figurewidth}{0.8\columnwidth}
   \setlength{\figureheight}{0.68\figurewidth}
   \input{\thisDir/figs/LPMfig.tikz}
   \caption[Illustration of the LPM.]{Illustration of the \gls{LPM}. Top figures: input spectrum (left) and output spectrum (right). 
   A small band is selected (gray area), in which $\hat G_{\LPM}(\omega_{k+r})$ is estimated (black thick line, bottom figure) as a local polynomial. Only its central value $\hat G_{\LPM}(\omega_k)$ (white circle) is retained. This procedure is repeated for all frequencies $\omega_k$.}
   \label{LPM_Schematic_EG}
\end{figure}
This procedure is repeated at each central frequency $\omega_k$ for  $k\in \Set{1,\dots,N/2}$ (i.e. the entire frequency band, including Nyquist, but excluding \gls{DC}, and regularizing at the boundaries). This completes the \gls{LPM}, yielding an intrinsic averaging of the spectra of the estimated \gls{FRF}, $\hat{G}_{\LPM}(\omega_k)$.

@@

\end{enumerate}
This procedure is illustrated in \figref{fig:nparam:trunc:nonparametric:truncation:Ftest} for the system described by the following equations, which are relevant to the \gls{LPM} outlined in \secref{sec:nparam:trunc:LPMFRFest}:
\begin{subequations}
\label{eq:trunc:systemODEs}
\begin{align}
y_0(t)  &= 1.5371y_0(t-1)    -0.9025y_0(t-2) + u(t)\\
y(t)       &= y_0(t) + e(t),
\end{align}
\end{subequations}
where $e(t)$ is a white noise sequence, such that the SNR of the output signal is $78.2\unit{dB}$.
The figure shows segments of the estimated impulse response. The last two segments are dominated by the noise, while all samples at $t<80$ have large system contributions. The algorithm outlined above selects $\truncTime = 80$, beyond which all samples are set to zero, resulting in a smoothed \gls{FRF} estimate.

@@

\figref{fig:nparam:trunc:LPMvsTRunc} and \figref{fig:nparam:trunc:pdfAndRMSeVStruncTime} compare the \gls{LPM} with and without truncation of the impulse response.
Here, the truncation instant $\truncTime$ is determined using the exponential fitting method.
They were obtained from simulations on the system in \eqref{eq:trunc:systemODEs} where the noise variance was set such that the \gls{SNR} of the output signal is $18.3\unit{dB}$.

### 2016-04-27 ch06-concl/conclusions.tex
More conclusion + small stuff everywhere

\section{Conclusions of this research}

@@

\section{Future perspectives}
  \subsection{Excitation design}
  In this thesis, quasi-logarithmic multisines were proposed as a robust excitation signal that provide efficient estimation of sharp resonance peaks in the \gls{SISO} case.
  Obviously, a first important extension of this research is towards the \gls{MIMO} case which is more involved.
  To measure \gls{MIMO} systems using multisines, one of two typical approaches is often followed when measuring all channels at the same time~\citep[Section 2.7]{Pintelon2012}:
  \begin{itemize}
    \item Zippered multisines, where the frequency grids of the different input channels are interspersed. This has the downside that frequency resolution is traded in for computational simplicity and that the different entries in the \gls{FRF} matrix are known on different frequency grids.
    \item Orthogonal multisines, which are computationally more involved to process, require multiple experiments but allow for finer frequency resolution.
  \end{itemize}
  Due to the intrinsic sparsity of quasi-logarithmic grids, however, zippered quasi-logarithmic multisines might offer an easy and elegant  approach to measure \gls{MIMO} systems with a moderate number of inputs.

@@

  \subsection{Non-parametric estimators}
    The \gls{LRM} has only been explored for \gls{SISO} systems in this thesis.
    This technique can obviously be extended towards \gls{MIMO} systems, e.g. as the work by \citet{vanRietschoten2015MSc} has shown.
    As explored there, the choice of parametrization remains an open question for the \gls{MIMO} case.
    Also, unlike the \gls{SISO} case, it becomes more important and tedious to select good local models since the dimensionality of the local estimation problem grows with the system dimensions.
    Extension to the \gls{MIMO} case, moreover, may directly lead to an approach that is able to deal with concatenated data records similarly to what the \gls{LPM} is able to provide.

@@

    Another application where the \gls{LPM} is more developed is the handling of missing data~\citep{Ugryumova2015}.
    In particular, the frequency domain relationship between the input $U$ and output $Y$ is augmented by a term $M_Y$ that accounts for the missing output data samples:
    \begin{equation}
      Y(\omega_k) = G(\omega_k) U(\omega_k) + T(\omega_k) + M_Y(\omega_k) + \mathrm{noise}\text{,}
    \end{equation}
    since $G(\omega_k)$ is captured by local polynomials, this allows to construct a design matrix as discussed in \chapref{sec:nonparametric} which only depends on $U$ and the time instances where the data is missing.
    For the \gls{LRM}, on the other hand, the design matrix depends on the output $Y$ which is not known.
    Consequently, extending the \gls{LRM} to handle missing data is non-trivial.

@@

  \subsection{Non-parametric estimation and interpolation}
  As with the regular \gls{LRM}, a major objective for future research is to extend the estimation approach of the $\Hinf{}$ gain towards the \gls{MIMO} case.
  In that context, the design of weighting filter also becomes even more important~\citep{Boeren2013}.
  Hence, the link between local models and the design of weighting filters and parametric overbounds needs to be made more explicit and verified experimentally.

@@

  \subsection{Parametric initialization}
  In \chapref{sec:initvals} it was already illustrated that smoother can provide improved initial estimates of a system. 
  Intrinsically, this stems from the fact that the effective \gls{SNR} of the transfer function is improved by means of the smoothness assumption and, on the other hand by the reduction in the the dimensionality in the parameter space.
  By no means were the  smoothers studied in \chapref{sec:initvals} chosen in an optimal way, such that it remains an open topic to determine which smoother has the best chance to produce good initial values in practical settings.

>>>>

@@

\section{Future Perspectives}
  \subsection{Excitation Design}
  In this thesis, quasi-logarithmic multisines were proposed as a robust excitation signal that provide efficient estimation of sharp resonance peaks in the \gls{SISO} case.
  Obviously, a first important extension of this research is towards the \gls{MIMO} case which is more involved.
  To measure \gls{MIMO} systems using multisines, one of two typical approaches is often followed when measuring all channels at the same time~\citep[Section 2.7]{Pintelon2012}:
  \begin{itemize}
    \item Zippered multisines, where the frequency grids of the different input channels are interspersed. This has the downside that frequency resolution is traded in for computational simplicity and that the different entries in the \gls{FRF} matrix are known on different frequency grids.
    \item Orthogonal multisines, which are computationally more involved to process, require multiple experiments but allow for finer frequency resolution.
  \end{itemize}
  Due to the intrinsic sparsity of quasi-logarithmic grids, however, zippered quasi-logarithmic multisines might offer an easy and elegant  approach to measure \gls{MIMO} systems with a moderate number of inputs.

@@

  \subsection{Non-parametric Estimators}
    The \gls{LRM} has only been explored for \gls{SISO} systems in this thesis.
    This technique can obviously be extended towards \gls{MIMO} systems, e.g. as the work by \citet{vanRietschoten2015MSc} has shown.
    As explored there, the choice of parametrization remains an open question for the \gls{MIMO} case.
    Also, unlike the \gls{SISO} case, it becomes more important and tedious to select good local models since the dimensionality of the local estimation problem grows with the system dimensions.
    Extension to the \gls{MIMO} case, moreover, may directly lead to an approach that is able to deal with concatenated data records similarly to what the \gls{LPM} is able to provide.

    As has been seen in \chapref{sec:nonparametric}, the \gls{LRIC} is affected by a high variance.
    This is due to pole-zero cancellations that arise when the local bandwidth does not contain data that is informative enough to estimate models of the required complexity.
    As such, future research needs to be undertaken to overcome such hurdles, by means of model order selection or reduction of those local models.
    If these hurdles can be overcome, the bias of local modeling can be reduced significantly.
    This is important for short datasets with very noisy data.

    Specifically for the \gls{LRM}, currently a model structure that is equivalent to rational forms in continuous time, i.e. the (local) transfer function model is isomorphic with
    \begin{equation}
      \LocalModel[\CT]{G}(\dW) 
      = \frac{\LocalModel{B}(\dW)}{\LocalModel{A}(\dW)}
      = \frac{\Sum_i  b_i \dW^{i}}{\Sum_i  a_i \dW^{i}}
    \end{equation}
    There have already been some experiments with other model structures such as local discrete time models where
    \begin{equation}
      \LocalModel[\DT]{G}(\dW) 
      = \frac{\LocalModel{B}(\dW)}{\LocalModel{A}(\dW)}
      = \frac{\Sum_i  b_i \exp ji\dW\Ts)}{\Sum_i  a_i \exp ji\dW\Ts }
    \end{equation}
    but these have proven more difficult to estimate numerically and hence unreliable.
    A possible approach for this would be to use orthogonal polynomials~\citep{Forsythe1957,Bultheel2005} for complex coefficients.

@@

    Another application where the \gls{LPM} is more developed is the handling of missing data~\citep{Ugryumova2015}.
    In particular, the frequency domain relationship between the input $U$ and output $Y$ is augmented by a term $M_Y$ that accounts for the missing output data samples:
    \begin{equation}
      Y(\omega_k) = G(\omega_k) U(\omega_k) + T(\omega_k) + M_Y(\omega_k) + \mathrm{noise}\text{,}
    \end{equation}
    since $G(\omega_k)$ is captured by local polynomials, this allows to construct a design matrix as discussed in \chapref{sec:nonparametric} which only depends on $U$ and the time instances where the data $y(t)$ is missing.
    For the \gls{LRM}, on the other hand, the design matrix depends on the output $Y$ which is not known.
    Consequently, extending the \gls{LRM} to handle missing data is non-trivial and could be an interesting topic for further research.

@@

  \subsection{Non-parametric Estimation and Interpolation}
  As with the regular \gls{LRM}, a major objective for future research is to extend the estimation approach of the $\Hinf{}$ gain towards the \gls{MIMO} case.
  In that context, the design of weighting filter also becomes even more important~\citep{Boeren2013}.
  Hence, the link between local models and the design of weighting filters and parametric overbounds needs to be made more explicit and verified experimentally.

@@

  \subsection{Construction of Initial Values}
  In \chapref{sec:initvals} it was already illustrated that smoother can provide improved initial estimates of a system. 
  Intrinsically, this stems from the fact that the effective \gls{SNR} of the transfer function is improved by means of the smoothness assumption and, on the other hand by the reduction in the the dimensionality in the parameter space.
  By no means were the  smoothers studied in \chapref{sec:initvals} chosen in an optimal way, such that it remains an open topic to determine which smoother has the best chance to produce good initial values in practical settings.
